Regularising Lotka--Volterra Interaction Matrices by Species Grouping

### 2021-10-23 article.rnw
Add a final pargraph of specific aims to the introduction.

>>>>

I propose that groups might be selected without regard to any \emph{a priori} definition, based purely upon which gives the most parsimonius model.
In this study, I investigate the usefulness and correctness of such a selection, using experimental \emph{Drosophila} fecundity data provided by \textcite{terry2021natural}.
I fit the Lotka--Volterra model, with grouped species, to find the grouping that gives the most parsimonious model.
I group species independently with regard to their effects upon other species and their responses to other species, to find whether the appropriate groupings might differ for these two cases.
Finally, I compare the resultant groupings with species phylogeny, to provide further investigation of the suitability of \emph{a priori} phylogenetic grouping.
